### 2024-02-19 documentation/thesis/thesis_document.tex
.

The use cases are defined during project planning and provide an
overview of how the user interacts with the project and what
functionalities can be expected. In the later accomplished evaluation
process in chapter \ref{use-case-evaluation}, the defined use cases are
also used as a reference to demonstrate the implemented capabilities of
the solution. This is essential for understanding the needs of the
target group and designing the result accordingly.

@@

The \gls{cli} mode is a simple text-based interface with which it is
possible to read out current measured values, obtain debug information
and set operating parameters. This allows to quickly inspect whether the
hardware is working properly after firmware installation. The command
\emph{help}, displays a detailed command reference with all available
commands as shown in the figure
\ref{Unified_sensor_firmware_provided_serial_terminal_based_(+cli)_allows_the_user_to_configure_the_sensor_manually.png}
to the user. The figure
\ref{Result_of_an_executed_b_value_measurement_readout_command_using_the_sensors_(+cli)_with_immediate_user_readable_response.png}
shows the current measured value queried by using the \emph{readout}
command by the user.

@@

One problem with the use of several sensors on one readout host \gls{pc}
is that the measurements may drift over time. On the one hand, \gls{usb}
latencies can occur. This can occur due to numerous factors, including
device drivers, data transfer speed and system resources. High-quality
\gls{usb} devices and modern drivers often minimise
latencies.\customcite{W19} Nevertheless, complex data processing tasks and
overloaded \gls{usb} ports can lead to delays.

@@

A jitter time of up to an additional \emph{1ms} is added between the
triggering of the measurements by the host system and the receipt of the
command by the sensor hardware. If the host system is still under load,
this value increases many times over. This means that synchronising
several sensors via the \gls{usb} connection alone is not sufficient.
The other issue is sending the trigger signal from the readout software,
which is described in chapter \ref{software-readout-framework}. At this
point unpredictable latencies can occur, too, depending on which other
tasks are also executed on this port.

To enable the most stable possible synchronisation between several
sensors, an option has already been created to establish an electrical
connection between sensors. This is used together with the firmware to
synchronise the readout intervals. The figure
\ref{Multi_sensor_synchronisation_wiring_example_using_three_sensors_together_with_one_host_(+pc)_performing_the_triggering_and_readout_processing.png}
illustrates the schematic how several sensors must be wired together to
implement this form of synchronisation.

@@

Since the \emph{MMC5603NJ} only has limited measurement range of total
\emph{6mT}, even small coin sized neodymium magnets already saturates
the sensor. It is possible to mount 3D printed spacers (see green part
in figure
\ref{Manufactured_1D_sensor_construction_from_different_angles_and_universal_magnet_mount_(green_3D_printed_part)_equipped_with_N45_12x12x12mm_magnet.png})over
the sensor to increase the distance between the magnet and the sensor
and thus also measure these magnets. The designed magnet holder can be
adapted for different magnet shapes and can be placed on the spacer
without backlash to be able to perform a repeatable measurement without
introducing measurement irregularities by mechanically changing the
magnet.

@@

As the sensors shown so far relate exclusively to self-built, low-cost
hardware, the following chapter shows how existing hardware can be
integrated into the system. A temperature-compensated \emph{Voltcraft
GM-70} telsameter shown in figure
\ref{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board_using_a_(+usb)_to_serial_converter_and_needed_additional_pull-up_resistors.png}
is used, which has a measuring range of \emph{0T} to \emph{3T} with a
resolution of \emph{0.1mT}. It offers an \emph{RS232} interface with a
documented protocol for connection to a \gls{pc}. This connectivity
makes it possible to make the device compatible with the previously
build unified sensor firmware using a separate
\href{https://github.com/RBEGamer/VoltcraftGM70Rest}{VoltcraftGM70Rest interface software}
executable on the host \gls{pc}. However, it does not offer the range of
functions that the unified sensor firmware offers.

Another option is a custom interface board between the meter and the PC.
This is a good option as many modern \gls{pc}s or \gls{sbc}s no longer
offer a physical \emph{RS232} interface. As with the other sensors, this
interface consists of a \emph{Raspberry Pi Pico} with an additional
level shifter. The teslameter is connected to the microcontroller using
two free \gls{gpio}s in \gls{uart} mode. The firmware is adapted using a
separate build configuration. In order to be able to read and correctly
interpret the data from the microcontroller, the serial protocol of the
sensor is implemented in a customised version of the \emph{CustomSensor}
class as shown in listing \ref{lst:CustomSensorClass}. This software or
hardware integration can be conducted on any other measuring device with
a suitable communication interface and a known protocol thanks to the
modular design.

@@

The \emph{HalbachMRIDesigner} \customcite{MWO24} is an opensource project
and generates basic \gls{cad} drawings for \gls{mri} magnets in a
Halbach configuration. To do this, the number of magnets and additional
parameters for the properties of the \gls{cad} model to be created are
passed to the function provided as input parameters using a \gls{json}
file. The result is an \emph{OpenSCAD} \customcite{MMN19} based 3D model
of the magnet holder.

@@

\begin{lstlisting}[caption={JSON structure of an exported MRPReading based measurement with information about the measurement environment, additional meta-data and raw data value objects}, label=lst:json_export_format_example]
{
  "time_start": "Wed Sep 20 08:50:13 2023",
  "time_end": "Wed Sep 20 08:54:13 2023",
  "additional_data": {
      "sensor_device_path": "/dev/ttyUnifiedSensorSingle",
      "sensor_name": "Unified Sensor Single Sensor",
      "sensor_id": "386731533439",
      "sensor_capabilities": ["static", "axis_b", "axis_x", "axis_y", "axis_z", "axis_temp", "axis_stimestamp"],
      "configname": "calibrationtemp30.yaml",
      "runner": "cli"
  },
  "data": [{
      "value": 0.135,
      "is_valid": true,
      "id": 0,
      "temperature": 34.32
  }],
  "measurement_config": {
      "id": "525771256544952",
      "sensor_distance_radius": 40.0,
      "magnet_type": 0
  },
  "name": "calibrationtemp30",
}
\end{lstlisting}

@@

Another application example is when sensors are physically separated or
there are long distances between them. By connecting several sensors via
the proxy module, it is possible to link several instances and all
sensors available in the network are accessible to the \emph{control}
\gls{pc}.

@@

Figure \ref{Example_MRP_proxy_module_usage_using_two_remote_(+pc)s.png}
shows the modified \emph{multi-proxy - multi-sensor} topology. Both
proxy instances do not communicate directly with the \emph{control}
\gls{pc}, but the proxy instance \emph{remote} \gls{pc} \emph{\#2} can
access the proxy running on \emph{remote} \gls{pc} \emph{\#1}.

The \emph{control} \gls{pc} only communicates with the \emph{remote}
\gls{pc} \emph{\#1}, but can access all sensors in this chain.

@@

Immediately after starting the \emph{MRPProxy}, the \gls{uuid}s of all
locally connected sensors are read out. These are stored together with
the class instance of the \emph{MRPHal} module in a \gls{lut}. This
makes it possible to address and interact with a sensor directly using
its \gls{uuid}.

@@

When using sensors with the same capabilities, these must be combined.
These are used to select the appropriate measurement mode for a
measurement. For this purpose, the \emph{info} command of each sensor is
queried. This information is added to the previously created \gls{lut}.
Duplicate entries are summarised (see table
\ref{Sensor_capabilities_merging_algorithm.csv}) and returned to the
host when the \emph{info} \ref{lst:mtsc} command is received over
network.

@@

If no hardware sensor is available for the generation of test data, the
\emph{MRPSimulation} module is available. This contains a series of
functions that simulate various magnets and their fields. The result is
a complete \emph{MRPReading} measurement with a wide range of set meta
data. The example listing \ref{lst:mrpexample_simulation} illustrates
the basic usage. Different variations of the \emph{generate\_reading}
function offer the user additional parameterisation options, such as
random polarisation direction or a defined centre-of-gravity vector. The
data is generated in the background using the \emph{magpylib}
\customcite{OB20} library according to the specified parameters.

@@

The following example listing \ref{lst:mrpexample_halbach} shows how a
simple Halbach magnetic ring can be generated. This can be used to
construct a Halbach ring magnet (see chapter \ref{magnet-system}) for a
low-field \gls{mri}.

Eight random measurements are generated at this point. It is important
that the magnet type (for example \emph{N45\_CUBIC\_15x15x15}) is
specified. This is necessary so that the correct magnet cutouts can be
generated when creating the 3D model. After the measurements have been
generated, they are provided with a position and rotation offset
according to the Halbach design and calculation scheme \customcite{O24}
using the \emph{MRPHalbachArrayGenerator} module.

@@

Usability improvements in software libraries are essential for efficient
and user-friendly development. Intuitive API documentation, clearly
structured code examples and improved error messages promote a smooth
developer experience. A \gls{gui} or \gls{cli} application for complex
libraries can make it easier to use, especially for developers with less
experience. Continuous feedback through automated tests and
comprehensive error logs enable faster bug fixing.

@@

Thanks to this functionality of the \gls{cli}, it is now possible to
connect a sensor to the \gls{pc}, configure a measurement series with it
and run it at the end, which is shown in figure
\ref{MRP_(+cli)_output_to_configure_a_new_measurement.png}. The result
is an exported file with the measured values. These can then be read in
again using the \emph{MRPReading} module and processed further. The
following bash listing \ref{lst:MRPCli_config_run} shows the setup
procedure in detail:

@@

It is more applicable for users to carry out measurements using the
\gls{cli}-, the next logical step is to analyse the recorded data. This
can involve one or several hundred data records. Again, the procedure
for the user is to write their own evaluation scripts using the
\gls{mrp}-library. This is particularly useful for complex analyses or
custom algorithms, but not necessarily for simple standard tasks such as
bias compensation or graphical plot outputs.

@@

For this purpose, \gls{cli} application is created further, to enable
the user to create and execute complex evaluation pipelines for
measurement data without programming. The figure
\ref{Example_measurement_analysis_pipeline.png} shows a typical
measurement data analysis pipeline, which consists of the following
steps:

@@

In order to implement such a pipeline, the\gls{yaml} file format is
chosen for the definition of the pipeline, as this is for
non-programmers to understand and can also be easily edited with a plain
text editor. Detailed examples can be found in the
\href{https://magneticreadoutprocessing.readthedocs.io/en/latest/}{documentation}.
The pipeline definition consists of sections which execute the
appropriate Python commands in the background.

The signatures in the \gls{yaml} file are called using reflection and a
real-time search of the loaded \emph{global()} functions
\href{https://docs.python.org/3/library/functions.html#globals}{symbol table}.
This system is capable to make all Python functions available to the
user. To simplify usage, a pre-defined list of verified functions for
use in pipelines is listed in the
\href{https://magneticreadoutprocessing.readthedocs.io/en/latest/}{documentation}.
The following pipeline definition in listing
\ref{lst:mrpuddp_example_yaml} shows the previously defined steps shown
in figure \ref{Example_measurement_analysis_pipeline.png} as \gls{yaml}
syntax.

@@

Difficulties arise with the parts of the \gls{mrp}-library that require
direct access to external hardware. These are, for example, the
\emph{MRPHal} and \emph{MRPHalRest} modules, which are required to read
out sensors connected via the network. Two different approaches are
used. In the case of local development, the test runs are carried out on
a \gls{pc} that can reach the network hardware and thus the test run
could be carried out with real data.

In the other scenario, the tests are to be carried out before a new
release in the repository based on
\href{https://github.com/features/actions}{GithubActions}. It has the
possibility to host local runner software, which then has access to the
hardware, but in this case a \gls{pc} must be permanently available for
this task. Instead, the hardware sensors are simulated by software and
executed via virtualisation on the services systems.

@@

One crucial point that improves usability for users is the simple
installation of all \gls{mrp} modules. As it is created in the Python
programming language, there are several public package registries where
users can provide their software modules.

For this purpose \href{https://pypi.org}{PyPI} figure
\ref{MagneticReadoutProcessing_library_hosted_on_PyPi.png} is the most
used package registry and offers direct support for the package
installation program \gls{pip} shown in listing
\ref{lst:setup_lib_with_pip}.

@@

To make the \gls{mrp} file structure compatible with the package
registry, Python provides separate installation routines that build a
package in an isolated environment and then provide an installation
\href{https://peps.python.org/pep-0427/}{wheel} archive. This can be
uploaded to the package registry. Since the \gls{mrp}-library requires
additional Python dependencies, which cannot be assumed to be already
installed on the target system, these must be installed prior to the
actual installation. These can be specified in the library installation
configuration \emph{setup.py} in listing \ref{lst:setup_py_req} for this
purpose.

@@

\begin{longtable}[]{@{}lllll@{}}
\caption{Overview of all characterised sensor properties
\label{Overview_of_all_characterised_sensor_properties.csv}}\tabularnewline
\toprule
Symbol & TLV493D & MMC5603NJ & Unit & Description\tabularnewline
\midrule
\endfirsthead
\toprule
Symbol & TLV493D & MMC5603NJ & Unit & Description\tabularnewline
\midrule
\endhead
\(\mu_{nl}\) & 0.79 & 0.00 & \% & Mean noise level\tabularnewline
\(\sigma_{nl}\) & 0.76 & 0.00 & \% & \gls{sd} noise level\tabularnewline
\(\mu_{rv}\) & 157.23 & -50.39 & \(\mu\)T & Mean sensor value
(Baseline)\tabularnewline
\(\sigma_{rv}\) & 172.00 & 0.20 & \(\mu\)T & \gls{sd} sensor
value\tabularnewline
\(\mu_{t}\) & 20.68 & 19.40 & \(^{\circ}\)C & Mean sensor
temperature\tabularnewline
\(\sigma_{t}\) & 0.53 & 0.00 & \(^{\circ}\)C & \gls{sd} sensor
temperature\tabularnewline
\(\mu_{trev}\) & 21.0 & 21.0 & \(^{\circ}\)C & Ambient
temperature\tabularnewline
\(\mu_{sl}\) & 0.25 & 0.04 & \% & Mean sensor linearity
deviation\tabularnewline
\(\sigma_{sl}\) & 3.64 & 0.56 & \% & \gls{sd} sensor
linearity\tabularnewline
\(\mu_{td}\) & -1.99 & -5.13 & \(\mu\)T / \(^{\circ}\)C & Mean sensor
temperature coefficients\tabularnewline
\bottomrule
\end{longtable}

>>>>

The use cases are defined during project planning and provide an
overview of how the user interacts with the project and what
functionalities can be expected.

In the later accomplished evaluation process in chapter
\ref{use-case-evaluation}, the defined use cases are also used as a
reference to demonstrate the implemented capabilities of the solution.

This is important in order to understand the needs of the target group
and design the result accordingly. For this purpose, these were defined
into the following blocks:

@@

The \gls{cli} mode is a simple text-based interface with which it is
possible to read out current measured values, obtain debug information
and set operating parameters. This allows to quickly inspect whether the
hardware is working properly after firmware installation. The command
\emph{help}, displays a detailed command reference with all available
commands as shown in the figure
\ref{Unified_sensor_firmware_provided_serial_terminal_based_(+cli)_allows_the_user_to_configure_the_sensor_manually.png}
to the user.

The figure
\ref{Result_of_an_executed_b_value_measurement_readout_command_using_the_sensors_(+cli)_with_immediate_user_readable_response.png}
shows the current measured value queried by using the \emph{readout}
command by the user.

@@

One problem with the use of several sensors on one readout host \gls{pc}
is that the measurements may drift over time. On the one hand, \gls{usb}
latencies can occur. This can occur due to numerous factors, including
device drivers, data transfer speed and system resources. High-quality
\gls{usb} devices and modern drivers often minimise
latencies.\customcite{WSB19} Nevertheless, complex data processing tasks
and overloaded \gls{usb} ports can lead to delays.

@@

A jitter time of up to an additional \emph{1ms} is added between the
triggering of the measurements by the host system and the receipt of the
command by the sensor hardware. If the host system is still under load,
this value increases many times over. This means that synchronising
several sensors via the \gls{usb} connection alone is not sufficient.
The other issue is sending the trigger signal from the readout software,
which is described in chapter \ref{software-readout-framework}. At this
point unpredictable latencies can occur, too, depending on which other
tasks are also executed on this port. To enable the most stable possible
synchronisation between several sensors, an option has already been
created to establish an electrical connection between sensors. This is
used together with the firmware to synchronise the readout intervals.
The figure
\ref{Multi_sensor_synchronisation_wiring_example_using_three_sensors_together_with_one_host_(+pc)_performing_the_triggering_and_readout_processing.png}
illustrates the schematic how several sensors must be wired together to
implement this form of synchronisation.

@@

Since the \emph{MMC5603NJ} only has limited measurement range of total
\emph{6mT}, even small coin sized neodymium magnets already saturates
the sensor. It is possible to mount 3D printed spacers (see green part
in figure
\ref{Manufactured_1D_sensor_construction_from_different_angles_and_universal_magnet_mount_(green_3D_printed_part)_equipped_with_N45_12x12x12mm_magnet.png})over
the sensor to increase the distance between the magnet and the sensor
and thus also measure these magnets.

The designed magnet holder can be adapted for different magnet shapes
and can be placed on the spacer without backlash to be able to perform a
repeatable measurement without introducing measurement irregularities by
mechanically changing the magnet.

@@

As the sensors shown so far relate exclusively to self-built, low-cost
hardware, the following chapter shows how existing hardware can be
integrated into the system. A temperature-compensated \emph{Voltcraft
GM-70} telsameter shown in figure
\ref{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board_using_a_(+usb)_to_serial_converter_and_needed_additional_pull-up_resistors.png}
is used, which has a measuring range of \emph{0T} to \emph{3T} with a
resolution of \emph{0.1mT}. It offers an \emph{RS232} interface with a
documented protocol for connection to a \gls{pc}. This connectivity
makes it possible to make the device compatible with the previously
build unified sensor firmware using a separate
\href{https://github.com/RBEGamer/VoltcraftGM70Rest}{VoltcraftGM70Rest interface software}
executable on the host \gls{pc}.

Another option is a custom interface board between the meter and the PC.
This is a good option as many modern \gls{pc}s or \gls{sbc}s no longer
offer a physical \emph{RS232} interface. As with the other sensors, this
interface consists of a \emph{Raspberry Pi Pico} with an additional
level shifter. The teslameter is connected to the microcontroller using
two free \gls{gpio}s in \gls{uart} mode. The firmware is adapted using a
separate build configuration.

In order to be able to read and correctly interpret the data from the
microcontroller, the serial protocol of the sensor is implemented in a
customised version of the \emph{CustomSensor} class as shown in listing
\ref{lst:CustomSensorClass}. This software or hardware integration can
be conducted on any other measuring device with a suitable communication
interface and a known protocol thanks to the modular design.

@@

The \emph{HalbachMRIDesigner} \customcite{MWO24} is an open-source project
and generates basic \gls{cad} drawings for \gls{mri} magnets in a
Halbach configuration. To do this, the number of magnets and additional
parameters for the properties of the \gls{cad} model to be created are
passed to the function provided as input parameters using a \gls{json}
file. The result is an \emph{OpenSCAD} \customcite{MMN19} based 3D model
of the magnet holder.

@@

\begin{lstlisting}[caption={JSON structure of an exported MRPReading based measurement with information about the measurement environment, additional meta-data and raw data value objects}, label=lst:json_export_format_example]
{
  "time_start": "Wed Sep 20 08:50:13 2023",
  "time_end": "Wed Sep 20 08:54:13 2023",
  "additional_data": {
      "sensor_device_path": "/dev/ttyUnifiedSensorSingle",
      "sensor_name": "Unified Sensor Single Sensor",
      "sensor_id": "386731533439",
      "sensor_capabilities": ["static", "axis_b", "axis_x", "axis_y", "axis_z", "axis_temp", "time"],
      "configname": "calibrationtemp30.yaml",
      "runner": "cli"},
  "data": [{
      "value": {"b":0.135},
      "id": 0,
      "temperature": 34.32}],
  "measurement_config": {
      "sensor_distance_radius": 40.0,
      "magnet_type": 1// CUBIC 12x12x12mm N45
  },}
\end{lstlisting}

@@

Another application example is when sensors are physically separated or
there are long distances between them. By connecting several sensors via
the proxy module, it is possible to link several instances and all
sensors available in the network are accessible to the \emph{control}
\gls{pc} by routing the requests through each \emph{control} \gls{pc} in
the chain to the target.

@@

Figure \ref{Example_MRP_proxy_module_usage_using_two_remote_(+pc)s.png}
shows the modified \emph{multi-proxy - multi-sensor} topology. Both
proxy instances do not communicate directly with the \emph{control}
\gls{pc}, but the proxy instance \emph{remote} \gls{pc} \emph{\#2} can
access the proxy running on \emph{remote} \gls{pc} \emph{\#1}. The
\emph{control} \gls{pc} only communicates with the \emph{remote}
\gls{pc} \emph{\#1}, but can access all sensors in this chain thought

@@

@@

Immediately after starting the \emph{MRPProxy}, the \gls{uuid}s of all
locally connected sensors are read out. These are stored together with
the class instance of the \emph{MRPHal} module in a \gls{lut}. This
makes it possible to address and interact with a sensor directly using
its \gls{uuid}. When using sensors with the same capabilities, these
must be combined. These are used to select the appropriate measurement
mode for a measurement. For this purpose, the \emph{info} command of
each sensor is queried. This information is added to the previously
created \gls{lut}. Duplicate entries are summarised (see table
\ref{Sensor_capabilities_merging_algorithm.csv}) and returned to the
host when the \emph{info} \ref{lst:mtsc} command is received over
network.

@@

If no hardware sensor is available for the generation of test data, the
\emph{MRPSimulation} module is available. This contains a series of
functions that simulate various magnets and their fields. The result is
a complete \emph{MRPReading} measurement with a wide range of set meta
data.

The example listing \ref{lst:mrpexample_simulation} illustrates the
basic usage. Different variations of the \emph{generate\_reading}
function offer the user additional parameterisation options, such as
random polarisation direction or a defined centre-of-gravity vector. The
data is generated in the background using the \emph{magpylib}
\customcite{OB20} library according to the specified parameters.

@@

The following example listing \ref{lst:mrpexample_halbach} shows how a
simple Halbach magnetic ring can be generated. This can be used to
construct a Halbach ring magnet (see chapter \ref{magnet-system}) for a
low-field \gls{mri}. Eight random measurements are generated at this
point. It is important that the magnet type (for example
\emph{N45\_CUBIC\_15x15x15}) is specified. This is necessary so that the
correct magnet cutouts can be generated when creating the 3D model.

After the measurements have been generated, they are provided with a
position and rotation offset according to the Halbach design and
calculation scheme \customcite{O24} using the
\emph{MRPHalbachArrayGenerator} module.

@@

Usability improvements in software libraries are essential for efficient
and user-friendly development. Intuitive API documentation, clearly
structured code examples and improved error messages promote a smooth
developer experience. A \gls{gui} or \gls{cli} application for complex
libraries can make them more user-friendly, especially for developers
with less experience. Continuous feedback through automated tests and
comprehensive error logs enable faster bug fixing.

@@

As a result of this implemented functionality of the \gls{cli}, it is
now possible to connect a sensor to the \gls{pc}, configure a
measurement series with it and run it at the end, which is shown in
figure \ref{MRP_(+cli)_output_to_configure_a_new_measurement.png}. The
result is an exported file with the measured values. These can then be
read in again using the \emph{MRPReading} module and processed further.
The following bash listing \ref{lst:MRPCli_config_run} shows the setup
procedure in detail:

@@

@@

It is more applicable for users to carry out measurements using the
\gls{cli}-, the next logical step is to analyse the recorded data. This
can involve one or several hundred data records. Again, the procedure
for the user is to write their own evaluation scripts using the
\gls{mrp}-library. This is particularly useful for complex analyses or
custom algorithms, but not necessarily for simple standard tasks such as
bias compensation or graphical plot outputs. For this purpose, \gls{cli}
application is created further, to enable the user to create and execute
complex evaluation pipelines for measurement data without programming.
The figure \ref{Example_measurement_analysis_pipeline.png} shows a
typical measurement data analysis pipeline, which consists of the
following steps:

@@

In order to implement such a pipeline, the\gls{yaml} file format is
chosen for the definition of the pipeline, as this is for
non-programmers to understand and can also be easily edited with a plain
text editor. Detailed examples can be found in the
\href{https://magneticreadoutprocessing.readthedocs.io/en/latest/}{documentation}.
The pipeline definition consists of sections which execute the
appropriate Python commands in the background. The function signatures
in the \gls{yaml} file are called using reflection and a real-time
search of the loaded \emph{global()} functions
\href{https://docs.python.org/3/library/functions.html#globals}{symbol table}.
This system is capable to make all Python functions available to the
user. To simplify usage, a pre-defined list of verified and tested
functions for use in pipelines is listed in the
\href{https://magneticreadoutprocessing.readthedocs.io/en/latest/}{documentation}.
The following pipeline definition in listing
\ref{lst:mrpuddp_example_yaml} shows the previously defined steps shown
in figure \ref{Example_measurement_analysis_pipeline.png} as \gls{yaml}
syntax.

@@

Difficulties arise with the parts of the \gls{mrp}-library that require
direct access to external hardware. These are, for example, the
\emph{MRPHal} and \emph{MRPHalRest} modules, which are required to read
out sensors connected via the network. Two different approaches are
used:

\begin{itemize}
\item
  \textbf{Local Test Execution}: In the case of local development, the
  test runs are carried out on a \gls{pc} that can reach the network
  hardware and thus the test run could be carried out with real data.
\item
  \textbf{Remote Test Execution}: In the other scenario, the tests are
  to be executed out before a new published release in the repository
  based on \href{https://github.com/features/actions}{GithubActions}. It
  has the possibility to host local build (runner) software, which then
  has access to the hardware, but in this case a \gls{pc} must be
  permanently available for this task. Instead, the hardware sensors are
  simulated by software and executed via virtualisation on the services
  systems. The simulation of the hardware is implemented using \gls{usb}
  emulation, which uses a \gls{lut} to provide the expected or incorrect
  feedback.
\end{itemize}

@@

One crucial point that improves usability for users is the simple
installation of all \gls{mrp} modules. As it is created in the Python
programming language, there are several public package registries where
users can provide their software modules. For this purpose
\href{https://pypi.org}{PyPI} figure
\ref{MagneticReadoutProcessing_library_hosted_on_PyPi.png} is the most
used package registry and offers direct support for the package
installation program \gls{pip} shown in listing
\ref{lst:setup_lib_with_pip}.

@@

To make the \gls{mrp} file structure compatible with the package
registry, Python provides separate installation routines that build a
package in an isolated environment and then provide an installation
\href{https://peps.python.org/pep-0427/}{wheel} archive. This can be
uploaded to the package registry.

Since the \gls{mrp}-library requires additional Python dependencies,
which cannot be assumed to be already installed on the target system,
these must be installed prior to the actual installation. These can be
specified in the library installation configuration \emph{setup.py} in
listing \ref{lst:setup_py_req} for this purpose.

@@

\begin{longtable}[]{@{}lllll@{}}
\caption{Overview of all characterised sensor properties
\label{Overview_of_all_characterised_sensor_properties.csv}}\tabularnewline
\toprule
Symbol & TLV493D & MMC5603NJ & Unit & Description\tabularnewline
\midrule
\endfirsthead
\toprule
Symbol & TLV493D & MMC5603NJ & Unit & Description\tabularnewline
\midrule
\endhead
\(\mu_{nl}\) & 0.79 & 0.00 & \% & Mean noise level\tabularnewline
\(\sigma_{nl}\) & 0.76 & 0.00 & \% & \gls{sd} noise level\tabularnewline
\(\mu_{rv}\) & 157.23 & -50.39 & \(\mu\)T & Mean Baseline without offset
compensation\tabularnewline
\(\sigma_{rv}\) & 172.00 & 0.20 & \(\mu\)T & \gls{sd} sensor
value\tabularnewline
\(\mu_{t}\) & 20.68 & 19.40 & \(^{\circ}\)C & Mean sensor
temperature\tabularnewline
\(\sigma_{t}\) & 0.53 & 0.00 & \(^{\circ}\)C & \gls{sd} sensor
temperature\tabularnewline
\(\mu_{trev}\) & 21.0 & 21.0 & \(^{\circ}\)C & Ambient
temperature\tabularnewline
\(\mu_{sl}\) & 0.25 & 0.04 & \% & Mean sensor linearity
deviation\tabularnewline
\(\sigma_{sl}\) & 3.64 & 0.56 & \% & \gls{sd} sensor
linearity\tabularnewline
\(\mu_{td}\) & -1.99 & -5.13 & \(\mu\)T / \(^{\circ}\)C & Mean sensor
temperature coefficients\tabularnewline
\bottomrule
\end{longtable}
